---
title: "Primer on Daggity"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Primer

Exercises from “Causal Inference in Statistics: A Primer” by Pearl, Glymour, and Jewell.

```{r installation}
library(dagitty)
library(lavaan)
```

## Preliminaries
### Study question 1.4.1

We first define the graph in this exercise using dagitty syntax and plot it.
You can also embed plots, for example:

```{r}
g <- dagitty('dag {
    X [pos="0,1"]
    Y [pos="1,1"]
    Z [pos="2,1"]
    W [pos="1,0"]
    T [pos="2,2"]
    
    X -> Y -> Z -> T
    X -> W -> Y -> T
    W -> Z
}')
plot(g)
```

a. Name all of the parents of $Z$.
```{r}
parents( g, "Z" )
```

b. Name all of the ancestors of $Z$.
```{r}
ancestors( g, "Z" )
```

c. Name all of the children of $W$.
```{r}
children( g, "W" )
```

d. Name all of the descendants of $W$.
```{r}
descendants( g, "W" )
```


e. Draw all simple paths between $X$ and $T$.
```{r}
paths( g, "X", "T" )$paths
```

f. Draw all the directed paths between $X$ and $T$.
```{r}
paths( g, "X", "T", directed=TRUE )$paths
```